---
title: "eds-221-day-3-1"
format: html
editor: visual
---pwd
---

## Conditional statement

```{r}
temperature <- 95

if (temperature >97) {
  print("Temperature warning")
 } else 
  print("No temperature warning")
```

Create an if else statement for blue whale lengths. Create a variable blue whale, which has a value of 40.

Add an if else statement that returns "GIANT" if exceeds 35, "MEDIUM" if the length is between 20 and 35, or "SMALL" if the length is \<=20.

```{r}
blue_whale <- 40

if (blue_whale > 35) {
  print("GIANT")
} else if (20 < blue_whale & blue_whale <= 35) {
    print("MEDIUM")
  } else if (blue_whale <=20) {
    print("SMALL")
  }
```

```{r}

```

## Switch statement

```{r}
housing_type <- "whole"

switch(housing_type, 
       "single" = print("400"),
       "double" = print("750"),
       "whole" = print("1100"))

if (housing_type == "whole") {
  print("1100")
} else if (housing_type == "double") {
  print("750")
} else if (housing_type == "single") {
  print("400")
}
```
