---
title: "eds-221-day-3-1"
format: html
editor: visual
---pwd
---

## Conditional statement

```{r}
temperature <- 95

if (temperature >97) {
  print("Temperature warning")
 } else 
  print("No temperature warning")
```

Create an if else statement for blue whale lengths. Create a variable blue whale, which has a value of 40.

Add an if else statement that returns "GIANT" if exceeds 35, "MEDIUM" if the length is between 20 and 35, or "SMALL" if the length is \<=20.

```{r}
blue_whale <- 40

if (blue_whale > 35) {
  print("GIANT")
} else if (20 < blue_whale & blue_whale <= 35) {
    print("MEDIUM")
  } else if (blue_whale <=20) {
    print("SMALL")
  }
```

## Switch statement

```{r}
housing_type <- "whole"

switch(housing_type, 
       "single" = print("400"),
       "double" = print("750"),
       "whole" = print("1100"))

if (housing_type == "whole") {
  print("1100")
} else if (housing_type == "double") {
  print("750")
} else if (housing_type == "single") {
  print("400")
}
```

## For loops

```{r}
height <- c(58, 61, 65, 72, 89, 94, 101)

for (i in seq_along(height)) {
  half_height = height[i]/2
  print(half_height)
}

# for each value in the height vector, return the sum of the value plus the one right after it
for (i in seq(1:(length(height)-1))) {
  height_add = height[i] + height[i + 1]
  print(height_add)
}

# write a for loop that calculates the value of height for each element divided by the mean of the entire height vector
for (i in seq_along(height)) {
  height_div = height[i]/mean(height)
  print(height_div)
}
```
